sdmTMB: an R package for fast, flexible, and accessible generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-06-06 doc/paper.Rmd
user-friendly -> accessible

title: "sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields"

>>>>

title: "sdmTMB: an R package for fast, flexible, and accessible generalized linear mixed effects models with spatial and spatiotemporal random fields"
